How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
intro

Scratch is a programming language developed to teach children programming by enabling them to create games and interactive animations. The public repository of Scratch programs contains over 12 million projects. Scratch is a \emph{block-based} language: users manipulate blocks to program. Block-based languages are visual languages, but also use some successful aspects of text-based languages such as limited text-entry and indentation, and as such are closer to `real', textual programming than other forms of visual programming, like dataflow languages are.

@@

refer to:
Research on the effectiveness of those languages for programming education
Research on programming habits
Our research on smells

>>>>

Scratch is a programming language developed to teach children programming by enabling them to create games and interactive animations. The public repository of Scratch programs contains over 12 million projects. Scratch is a \emph{block-based} language: users manipulate blocks to program.

@@

Several studies have shown that block-based languages are powerful as a tool for teaching programming~\cite{meerbaum-salant_learning_2010, b._moskal_evaluating_2005,cooper_teaching_2003}. \todo{Fenia, do you have some work on Research on programming habits}

Recent work has focused on \emph{code smells} within Scratch programs, parts of a program that are not designed in the best possible way. \todo{add dr. scratch papers here} Ar recent controlled experiment found that long scripts and duplication decreases a novice programmer's ability to understand and modify Scratch programs \todo{cite}.
